Analysis of transit delays in the Toronto Transit Commission: 2024

### 2024-09-25 paper/paper.qmd
Update paper.qmd

# Data {#sec-data}
## Data Source
## Data Measurement

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

Talk way more about it.

>>>>

# Data {#sec-data}
## Data Source
The data are gathered from Open Data Toronto's report on TTC delays. The datasets, published by the TTC, include: the first dataset, which presents delay statistics for subways in 2024; the second dataset, which details delay statistics for buses in 2024; and the third dataset, which provides delay statistics for streetcars in 2024.

# Data Analysis
The dataset provides information that offers insights of public transit delays across different types of transportation. The y-axis represents  The x-axis corresponds ,representing the total income for each year.

Additionally, data cleaning and analysis were conducted using the base statistical programming language R (R Core Team 2023), tidyverse (Wickham et al. 2019), ggplot2 (Wickham 2016), dplyr (Wickham et al. 2023), readr (Wickham, Hester, and Bryan 2023), tibble (Müller and Wickham 2023), janitor (Firke 2023), and knitr (Xie 2023) package were used.
